---
title: "Analyse code frequencies"
author: "Marie & Anna"
date: "2024-05-22"
output:
  html_document:
    highlight: zenburn
    theme: sandstone
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

# 1. Packages & Set-up

```{r warning=FALSE}
library(tidyverse) # Data handling
library(knitr) # For report
library(stringr)
```

We have one csv file per participant (containing all assigned codes).
They are stored in the same folder. Similar to how we use the app, we can specify where our project folder is stored and from which user we want to load the results. 

```{r}

Projectwd <- "/Users/annalangener/Nextcloud/Shared/Testing Methods to Capture Social Context/Qualitative context/3. Coding/QualitativeCoding_Activies/"
User <- "Marie_FullCoding"  # "Marie_FullCoding", "Marie", "Anna"

Data <- read.csv(paste(Projectwd,"Data/act_coding_ALL.csv",sep = ""))[,-1]
```

# 2. Reading in the Data & Results


Here we load these files and combine them into one dataframe:

```{r message=FALSE, warning=FALSE, include=FALSE}

list_of_files <- list.files(path = paste(Projectwd,User, sep = ""), pattern = "\\.csv$", full.names = TRUE) 
list_of_files <- list_of_files[-24] #last file is overview

codes <- list_of_files %>%
  setNames(nm = basename(.)) %>% 
  map_df(~read_csv(.x, col_types = cols(), col_names = TRUE), .id = "ID")

codes$ID <- str_extract(codes$ID , "\\d+")

codes <- codes %>% select(ID, Code, OtherComments, V3, V4)
colnames(codes) <- c("ID","Code","OtherComment","Feeling","Whom")
```

Here is some sample code to merge our results dataframe with the dataframe that contains the raw observations. We did not need to do this for our project, but it may be useful for some research projects. It is important to make sure that the participant IDs match. Depending on the order of the data, it may also be useful to loop through the participants to avoid errors (we did not do this ourselves, as the order already matched in both dataframes).

```{r message=FALSE, warning=FALSE, include=FALSE}

Data <- cbind(Data, codes)

sum(Data$ppID != Data$ID) # To check if they are correctly merged

Data <- Data %>% select(!ID)
```

Next, we will select only the variable with the actual codes and split it into separate rows to be able to calculate the frequencies of how often a code is used.

```{r}
codes %>% select(Code) -> codes

codes <- unlist(strsplit(codes$Code, " ;"))
codes <- trimws(codes)
codes<- as.data.frame(codes)
```

# 3. Check frequencies for each code

```{r}
 data.frame(table(codes$codes)) %>% arrange(desc(Freq)) -> Freq
```

# 4. Compare to tree codes

First load and format the data
```{r}
tree <- read.csv('Overview_Codes.csv',
                 row.names = NULL)

# only include level 1-3 codes

tree %>% select(Code, Level) %>% filter(Level !=4) -> tree

tree.codes <- tree$Code
freq.codes <- Freq$Var1
```

Now compare
```{r}
tree.codes[!(tree.codes %in% freq.codes)] 
```


